 % SPDX-License-Identifier: CC-BY-SA-4.0

\title{Aragon Network Community Guidelines}
\input{_header.tex}

\begin{document}
\mytitle

\section{Code of Conduct}

We as community members, contributors and leaders pledge to make participation in the Aragon Network a harassment-free experience for everyone, regardless of age, body size, visible or invisible disability, ethnicity, sex characteristics, gender identity and expression, level of experience, education, socio-economic status, nationality, personal appearance, race, religion, or sexual identity and orientation.
We pledge to act and interact in ways that contribute to an open, welcoming, diverse, inclusive, effective and healthy community for ourselves, each other, and the planet.


\section{Our Standards}
\label{sec:OurStandards}

\textbf{Examples of behaviour that contributes to a positive environment for our community include:}
\begin{itemize}
	\item Assuming good intentions and demonstrating empathy and kindness toward other people. 
	\item Being respectful of differing opinions, viewpoints, and experiences.
	\item Giving and gracefully accepting constructive feedback.
	\item Proactively taking responsibility.
	\item Clearly communicating if we might fail to uphold responsibility, working to avoid or repair negative consequences on others, adequately apologizing with the affected parties, and learning from the experience.
	\item Focusing on what is best not just for us as individuals, but for the overall community.
	\item Embodying the values of the Aragon Manifesto.
\end{itemize}
	
\textbf{Examples of unacceptable behaviour include:}
\begin{itemize}
	\item Selling or renting votes.
	\item Trolling, insulting or derogatory comments, and personal or political attacks.
	\item Public or private harassment, including stalking or repeated unwanted contact, including non-consensual sexual attention, sexualized language or imagery, or advances of any kind.
	\item Misleading or passive-aggressive comments.
	\item Publishing others' private information, including personal identifiable information such as a physical address or email address, without their explicit permission.
	\item Hate speech such as promotes violence or hatred against people based on characteristics like race, ethnicity, national origin, caste, religion, disability, disease, age, sexual orientation, gender, or gender identity.
	\item Doing any unlawful purpose or in furtherance of illegal activities.
	\item Spam (unsolicited off-topic messages, especially commercial in nature).
	\item Inciting or threatening violence, encourage, glorify or incite violence against anyone relate to extremism, terrorism, or human trafficking, directly or indirectly, or encouraging others to hurt themselves.
	\item Propose or make any payments or behave directly or indirectly in a way that results in a violation of applicable anti-corruption laws.
	\item Repeatedly yelling (i.e. ALL CAPS or excessive exclamation points!!!).
	\item Discussing the price of a token or asset, or giving any type of financial advice.
\end{itemize}


\section{Violations and Consequences}
\label{sec:ViolationsAndConsequences}
	
\glspl{CommunityMember} will follow the guidelines listed below, in determining the consequences for any action they deem in violation of the \hyperref[sec:CodeOfConduct]{Code of Conduct}:

\subsection{Correction}

\textbf{Community Impact:} A single use of inappropriate language or other behavior deemed unwelcome in the community.

\textbf{Consequence:} Deletion or removal of the post in question, in addition to communicating which rule was violated and how to avoid such violations in the future.
If the action was in person, direct communication with that individual to identify which rule was violated and how to avoid such violations in the future.


\subsection{Warning}

\textbf{Community Impact:} A violation through a single incident or series of actions.

\textbf{Consequence:} A warning with consequences for continued inappropriate behavior.
No interaction with the people involved, including unsolicited interaction with those enforcing the Code of Conduct, for a specified period of time.
This includes avoiding interactions in community spaces as well as external channels like Telegram, Discord, Reddit, Community Forum, etc.
Violating these terms may lead to a temporary or permanent ban.


\subsection{Temporary Ban}

\textbf{Community Impact:} A serious violation of community standards, including sustained inappropriate behavior.

\textbf{Consequence:} A temporary ban from any sort of interaction or public communication with the Community for a specified period of time.
No public or private interaction with the people involved, including unsolicited interaction with those enforcing the Code of Conduct, is allowed during this period.
Violating these terms may lead to a permanent ban.


\subsection{Permanent Ban}

\textbf{Community Impact:} Demonstrating a pattern of violation of community standards, including sustained inappropriate behavior, harassment of an individual, or aggression toward or disparagement of classes of individuals.
Vote-selling or vote-renting classifies for a permanent ban.

\textbf{Consequence:} Permanent removal from any sort of interaction or public communication with the Community for a specified period of time.
If an individual has alternate accounts, those may be removed as well.
No public or private interaction with the people involved, including unsolicited interaction with those enforcing the Code of Conduct, is allowed.


\section{Reporting and Enforcement}
\label{sec:ReportingAndEnforcement}
	
Every community member has a duty to promote the use of the \hyperref[chap:CommunityGuidelines]{Community Guidelines}, call to attention members of the community who come close to or violate the \hyperref[chap:CommunityGuidelines]{Guidelines} (as long as this doesn’t put their personal safety in jeopardy), and inform platform admins of violations.
Ultimate responsibility for enforcing the \hyperref[chap:CommunityGuidelines]{Community Guidelines} in each platform rests with the platform admins of each platform.
	
To report a violation of the \hyperref[chap:CommunityGuidelines]{Community Guidelines}, members can:
\begin{itemize}
	\item Tag a moderator in the platform where the violation has occurred,
	\item Email the moderators at \href{community@aragon.org}{community@aragon.org}
	\item Or, anonymously, fill the form at: \href{https://violation-reporting.aragon.org}{https://violation-reporting.aragon.org}
\end{itemize}

\end{document}
